### 2025-03-03 paper/paper.tex
ha

\section{はじめに}

@@

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション条件の例}
  \label{tab:sim-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 24 \, \,Mbps\, \\
    端末数 & 80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション諸元}
  \label{tab:sim-base-param}
  \begin{tabular}{c|c}
    \hline
    対応規格 & IEEE 802.11a/b/g \\ 
    \hline
    周波数 & a \; 5.2 \, \,$\mathrm{GHz}$\, \\
    & b/g \; 2.4 \, \,$\mathrm{GHz}$\, \\
    \hline
    ガードインターバル & 800 \, \,$\mathrm{ns}$\, \\
    \hline
    端末台数 & 1 ～ 80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション1パラメータ}
  \label{tab:sim1-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 24 \, \,Mbps\, \\
    端末数 & 1～80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション2パラメータ}
  \label{tab:sim2-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 6～54 \, \,Mbps\, \\
    端末数 & 1～80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

>>>>

\section{はじめに}
\subsection{背景}

@@

\subsection{目的}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション条件の例}
  \label{tab:sim-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60  \,$\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9  \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, $\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, $\mathrm{\mu s}$\, \\
    伝送レート & 24 \, Mbps\, \\
    端末数 & 80 \, 台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション諸元}
  \label{tab:sim-base-param}
  \begin{tabular}{c|c}
    \hline
    対応規格 & IEEE 802.11a/b/g \\ 
    \hline
    周波数 & a : 5.2  \,$\mathrm{GHz}$\, \\
    & b/g : 2.4  \,$\mathrm{GHz}$\, \\
    \hline
    ガードインターバル & 800  \,$\mathrm{ns}$\, \\
    \hline
    端末台数 & 1 ～ 80 \, 台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション1パラメータ}
  \label{tab:sim1-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, $\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9  \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, $\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, $\mathrm{\mu s}$\, \\
    伝送レート & 24 \, Mbps\, \\
    端末数 & 1～80 \, 台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション2パラメータ}
  \label{tab:sim2-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, $\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9 \, $\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, $\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, $\mathrm{\mu s}$\, \\
    伝送レート & 6～54 \, Mbps\, \\
    端末数 & 1～80 \, 台\, \\
    \hline
  \end{tabular}
\end{table}
